Individual Variation in Animal Movement

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
update and add citations for methods

>>>>

  The moveHMM package allows for fitting hmm models to different time series, which can come from different individuals, assuming that all individuals share the same movement models, meaning the same distributions and parameters for step length and angle. This is referred to as 'complete pooling' [@moveHMM, @langrock2012flexible, @michelot2016movehmm]
